%-------------------------
% Author: Nguyen Thi Yen Nhi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage[default]{inter}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape NGUYEN THI YEN NHI} \\ \vspace{1pt}
    \small \faicon{phone} (+84)326-583-876 $|$  \href{mailto:nhiyen.engineer@gmail.com}{\faicon{envelope} nhiyen.engineer@gmail.com} $|$ 
    \href{https://github.com/nguyenlephong}{\faicon{github} nhiney} $|$ 
    \href{https://www.linkedin.com/in/nhi-yen-410b2a2b7/}{\faicon{linkedin} nhi-yen-0906}
\end{center}

%-----------ABOUT-----------
\section{Summary}
    \resumeSubHeadingListStart

    \resumeItem{Third-year Information Technology student at Ho Chi Minh City University of Industry and Trade (\textbf{GPA 3.34/4.0}), expected to graduate in 2027, with a clear goal of becoming a \textbf{Fullstack Developer}. Strong interest in building complete systems from user interface to backend logic and database design.}

    \resumeItem{Frequently taking the \textbf{team lead role} in academic projects, responsible for requirement analysis, system design direction, task breakdown, and progress coordination. Focused on clean code organization, database structure, and system scalability rather than only feature completion.}

    \resumeItem{\textit{Core technical focus and project experience:}}
    
    \resumeItemListStart
      \resumeItem{\textbf{Backend:} Participated in building real-world academic systems including e-commerce websites (mobile phone shop, cosmetic shop), hotel management system, and an upcoming smart medical appointment booking system. Experienced in designing RESTful APIs, implementing authentication, role-based authorization, order/booking workflows, and input validation.}
      
      \resumeItem{\textbf{Databases:} Designed and implemented relational databases for commercial and management systems; handled table relationships, data consistency, and SQL queries supporting business logic.}
      
      \resumeItem{\textbf{Frontend:} Developed responsive web interfaces using \textbf{React} (TypeScript, Next.js); built reusable components, managed forms and validation, and integrated frontend with backend APIs.}
      
      \resumeItem{\textbf{Development Workflow:} Worked in team environments using Git, milestone-based task planning, and feature review before delivery.}
      
      \resumeItem{\textbf{Testing \& Quality:} Experienced in writing test cases, Test Plans, and performing functional testing to ensure feature stability before demo or submission.}
    \resumeItemListEnd
    
    \resumeSubHeadingListEnd
\vspace{8pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Smart Medical Appointment Booking Application} $|$ \emph{Flutter, Firebase, Cloud Functions}}{}
        \resumeItemListStart
            \resumeItem{Developing a mobile application connecting patients and doctors, enabling appointment booking and medical record management.}
            \resumeItem{Implemented \textbf{Firebase Authentication} for secure user login and role-based access (Patient/Doctor).}
            \resumeItem{Designed and structured \textbf{Firestore} database for managing users, schedules, appointments, and medical records.}
            \resumeItem{Integrated \textbf{Cloud Functions} to handle backend logic such as appointment confirmation, notifications, and data validation.}
            \resumeItem{Utilized \textbf{Google Maps API} to display hospital/clinic locations and support navigation features.}
            \resumeItem{Implemented medication reminders and appointment notifications to enhance user experience.}
            \resumeItem{\textbf{Technologies:} Flutter, Firebase (Auth, Firestore), Cloud Functions, Google Maps API}
        \resumeItemListEnd
        
        \vspace{8pt}
      \resumeProjectHeading
        {\textbf{Shoe Shop Management System} $|$ \emph{ASP.NET MVC, SQL Server, Razor, Bootstrap}}{}
        \resumeItemListStart
            \resumeItem{Developed a shoe shop management system following the \textbf{MVC architecture}.}
            \resumeItem{Designed and implemented a relational database with primary/foreign keys, \textbf{CHECK, UNIQUE, DEFAULT constraints}; created ERD and applied normalization.}
            \resumeItem{Implemented advanced SQL components including \textbf{Stored Procedures, Functions, Triggers, and Transactions} to handle business logic and ensure data consistency.}
            \resumeItem{Built authentication and \textbf{role-based authorization (Admin/Customer)} with account management and backup strategy.}
            \resumeItem{Developed complete e-commerce workflows: product management, search, shopping cart, order processing (COD), and revenue statistics.}
            \resumeItem{Developed responsive UI using Razor (.cshtml) and Bootstrap; applied AJAX interactions, server-side validation, password hashing, and SQL Injection prevention.}
            \resumeItem{\textbf{Technologies:} ASP.NET MVC, SQL Server, Razor, HTML5, CSS3, Bootstrap, JavaScript/jQuery}
        \resumeItemListEnd



        \vspace{8pt}          
        \resumeProjectHeading
        {\textbf{Sports Field Booking Management System} $|$ \emph{Laravel, PHP, MySQL, Blade, Bootstrap}}{}
        \resumeItemListStart
            \resumeItem{Developed a full-stack web application using \textbf{Laravel (MVC)} and \textbf{MySQL}.}
            \resumeItem{Designed a relational database schema and implemented \textbf{Eloquent ORM}, Migrations, and Seeders for structured data management.}
            \resumeItem{Implemented \textbf{authentication} and \textbf{role-based authorization (Admin/User)} using Laravel Auth and Middleware.}
            \resumeItem{Built complete \textbf{CRUD modules} for users, sports fields, schedules, bookings, and payments.}
            \resumeItem{Enhanced performance with search, pagination, and server-side validation.}
            \resumeItem{Developed a responsive UI using Blade Templates and Bootstrap.}
            \resumeItem{Applied \textbf{OOP principles} and RESTful routing standards.}
            \resumeItem{Used Git/GitHub for version control and team collaboration; configured local environment with Laragon.}
            \resumeItem{\textbf{Tools:} VS Code, Git, GitHub, Laragon}
        \resumeItemListEnd

      \vspace{8pt}

            \vspace{8pt}          
        \resumeProjectHeading
        {\textbf{English Vocabulary Learning Application} $|$ \emph{Python, Tkinter, JSON}}{}
        \resumeItemListStart
            \resumeItem{Developed a desktop application using \textbf{Python} and \textbf{Tkinter}, applying \textbf{OOP principles} to ensure maintainable and structured code.}
            \resumeItem{Designed a user-friendly GUI supporting full \textbf{CRUD operations} for vocabulary management.}
            \resumeItem{Implemented \textbf{JSON-based data storage} with safe read/write mechanisms to maintain data integrity.}
            \resumeItem{Integrated external data sources via web crawling or API consumption to enrich vocabulary content.}
            \resumeItem{Built \textbf{user authentication} and \textbf{role-based access control (Admin/User)}.}
            \resumeItem{Packaged the application into a standalone executable for easy deployment.}
            \resumeItem{\textbf{Tools:} VS Code, Git, GitHub}
        \resumeItemListEnd
        
        \vspace{8pt}
        
      \vspace{8pt} 
    
    \resumeSubHeadingListEnd

\vspace{8pt}

%-----------EXPERIENCE-----------
\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Programming Languages:} C\#, PHP, JavaScript, SQL, Python, Dart
    \item \textbf{Frameworks \& Libraries:} ASP.NET MVC, Laravel, Flutter, ReactJS, Entity Framework, Firebase
    \item \textbf{Databases:} SQL Server, MySQL, MongoDB, Redis, GraphDB, Oracle
    \item \textbf{Database Concepts:} Stored Procedures, Triggers, Transactions, ERD Design, Normalization
    \item \textbf{Web Development:} HTML5, CSS3, Bootstrap, jQuery, AJAX
    \item \textbf{Tools \& Platforms:} Git, GitHub, Docker, Visual Studio, VS Code, JetBrains Rider, WebStorm, Laragon
\end{itemize}

\vspace{6pt}
%-----------REFERENCES-----------
% \section{REFERENCES}
% \setlength{\tabcolsep}{-2pt}
% \begin{tabular}{l c r}

% % Referee NGO VAN KIM KHANH
% \begin{minipage}[t]{3in}
% \textbf{Mr. NGO VAN KIM KHANH}\\
% \textit{Co-founder \& Developer \& CEO, Algae} \\
% \textit{SRE \& Cloud/OnPrem Infrastructure}\\
% \textit{PrimeData VN}\\
% \Letter\ \href{mailto:khanh.ngo@algae.vn}{khanh.ngo@algae.vn}\\
% \Telefon\ (+84) 907-709-380\\
% \end{minipage}
% &

% % Referee LE NGOC QUOC HUY
% \begin{minipage}[t]{3in}
% \textbf{Mr. LE NGOC QUOC HUY}\\
% \textit{Former Director of Engineering \&} \\
% \textit{Co-founder, PrimeData VN} \\
% \Letter\ \href{mailto:huy.lenq@gmail.com}{huy.lenq@gmail.com} \\
% \Telefon\ (+84) 983-543-444
% \\ \href{https://www.linkedin.com/in/huylenq/}{\faicon{linkedin} huylenq} \\
% \end{minipage}

% &

% % Referee VU DUY HUNG

% \begin{minipage}[t]{3in}

% \textbf{Mr. VU DUY HUNG}\\
% \textit{Head Data Platform \&} \\
% \textit{Co-founder, PrimeData VN} \\
% \Letter\ \href{mailto:hung506khtn@gmail.com}{hung506khtn@gmail.com} \\
% \Telefon\ (+84) 845-640-394\\ ‬
% \href{https://www.linkedin.com/in/brian-vu-506}{\faicon{linkedin} brian-vu-506} \\


% \end{minipage}
% \\
% \\ % Additional newline for spacing.

% \end{tabular}

%-------------------------------------------
\end{document}
