%-------------------------
% Author: Nguyen Thi Yen Nhi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% \usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape NGUYEN THI YEN NHI} \\ \vspace{4pt}
    \small
    \faicon{phone} (+84) 326-583-876 $|$
    \href{mailto:nhiyen.engineer@gmail.com}{\faicon{envelope} nhiyen.engineer@gmail.com} $|$
    \href{https://github.com/nguyenlephong}{\faicon{github} nhiney} $|$
    \href{https://www.linkedin.com/in/nhi-yen-410b2a2b7/}{\faicon{linkedin} nhi-yen-0906}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
    \resumeSubHeadingListStart

        \resumeItem{
        Third-year Information Technology student at Ho Chi Minh City University of Industry and Trade (HUIT) (\textbf{GPA 3.34/4.0}), expected to graduate in 2027. Looking for a \textbf{Software Engineer Intern} role focused on backend systems and cloud platforms.
        }
        
        \resumeItem{
        Experience building \textbf{backend systems} and \textbf{database-driven applications}, including RESTful APIs, authentication, and role-based access control (RBAC), with a focus on \textbf{data consistency} and system reliability.
        }
        
        \resumeItem{
        Familiar with \textbf{Git-based workflows}, code reviews, and writing \textbf{30+ test cases}. Strong in \textbf{debugging and problem-solving}, with a step-by-step approach to improving system quality.
        }
        
        \resumeItem{
        Often take the \textbf{team lead role} in academic projects (3--5 members), contributing to requirement analysis, basic system design, task breakdown, and progress coordination.
        }
        
        \resumeItem{\textit{Core technical skills:}}
        
        \resumeItemListStart
          \resumeItem{\textbf{Backend:} Worked with \textbf{ASP.NET MVC} and \textbf{Laravel} to build RESTful APIs, authentication, RBAC, and backend workflows with validation and basic concurrency handling.}
          
          \resumeItem{\textbf{Databases:} Experience with \textbf{SQL Server}, \textbf{MySQL}, and \textbf{MongoDB}; familiar with schema design, constraints, transactions, and query optimization.}
          
          \resumeItem{\textbf{Programming:} Proficient in \textbf{C\#}, \textbf{PHP}, and \textbf{TypeScript/JavaScript}, applying \textbf{OOP} and writing modular code.}
          
          \resumeItem{\textbf{Tools \& Workflow:} Familiar with \textbf{Git}, code reviews, and basic use of \textbf{Docker}.}
          
          \resumeItem{\textbf{Concepts:} Understanding of RESTful design, debugging, and interested in learning cloud and system design.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{2pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeProjectHeading
        {\textbf{Smart Medical Booking App} $|$ \emph{Flutter, Firebase}}{\emph{Apr 2026 -- Present}}
        \resumeItemListStart
           \vspace{6pt}
            \resumeItem{\textbf{Project Overview:} Developed a mobile healthcare application that allows patients to book appointments, manage medical records, and search for dctors, with support for voice-assisted interactions.}
    
            \resumeItem{Led a team of \textbf{4 members} to design and develop the system, coordinating tasks and supporting feature delivery across the development process.}
            \resumeItem{Designed the \textbf{Firestore data model} for users, schedules, and appointments, ensuring \textbf{data consistency} in concurrent booking scenarios.}
            \resumeItem{Handled \textbf{concurrent booking requests} and implemented backend validation logic to prevent scheduling conflicts.}
            \resumeItem{Developed backend logic using \textbf{Cloud Functions} for appointment workflows, notifications, and server-side validation to ensure reliable system behavior.}
            \resumeItem{Implemented \textbf{Firebase Authentication} with secure login and \textbf{role-based access control} (Patient / Doctor / Admin).}
            \resumeItem{Integrated \textbf{Google Maps API} for clinic discovery and location-based search.}
           \resumeItem{Added a \textbf{voice-assisted booking feature} to help elderly and non-tech users interact with the system more easily.}
            \resumeItem{Wrote \textbf{100+ test cases} and debugged data flow issues to improve system stability and ensure smooth feature delivery.}
        \resumeItemListEnd
     
        
  \vspace{8pt}
       \resumeProjectHeading
        {\textbf{E-commerce Shoe Shop System} $|$ \emph{ASP.NET MVC, SQL Server}}{\emph{Dec 2025}}
        \resumeItemListStart
           \vspace{6pt}
                \resumeItem{\textbf{Project Overview:} Developed a full-stack e-commerce web application for online shoe shopping, supporting product browsing, order management, and secure user transactions.}
        
                \resumeItem{Led a team of \textbf{3 members} to design and build the system following \textbf{MVC architecture}.}
                
                \resumeItem{Designed a normalized relational database with \textbf{constraints (Check, Unique, Default)} to ensure data integrity and consistency.}
                
                \resumeItem{Used \textbf{Stored Procedures, Triggers, and Transactions} to enforce business rules and maintain data consistency during concurrent order processing.}
                
                \resumeItem{Built secure \textbf{authentication and role-based authorization} (Admin/Customer) with password hashing and protection against \textbf{SQL Injection}.}
                
                \resumeItem{Developed core features including product catalog, search \& filtering, shopping cart, and order processing (COD).}
                
                \resumeItem{Added \textbf{AI-assisted customer support} to provide basic product recommendations and handle common user inquiries.}
                
                \resumeItem{Used \textbf{AJAX} and server-side validation to improve user experience; optimized queries and resolved data consistency issues during testing.}

             \resumeItemListEnd
            
  \vspace{8pt}
       \resumeProjectHeading
        {\textbf{Sports Field Booking System} $|$ \emph{Laravel, MySQL}}{\emph{Nov 2025}}
        \resumeItemListStart
    \vspace{6pt}
            \resumeItem{\textbf{Project Overview:} Developed a web-based booking system that allows users to search, schedule, and reserve sports fields, while administrators can manage fields, bookings, and payments.}
    
            \resumeItem{Led a team of \textbf{4 members} to build the system, coordinating tasks and supporting progress during development.}
            
            \resumeItem{Built backend features using \textbf{Laravel (MVC)} with RESTful routing, using \textbf{Eloquent ORM}, Migrations, and Seeders for data management.}
            
            \resumeItem{Built \textbf{authentication and role-based authorization (Admin/User)} using Laravel Auth and Middleware.}
            
            \resumeItem{Developed \textbf{CRUD modules} for users, fields, schedules, bookings, and payments with validation and pagination.}
            
            \resumeItem{Handled booking logic to \textbf{avoid overlapping schedules} and ensure basic \textbf{data consistency}.}
            
            \resumeItem{Worked with Git/GitHub, participated in code reviews, and followed basic \textbf{OOP} and RESTful practices.}
            
            \resumeItem{Wrote \textbf{80+ test cases} and fixed issues found during testing to improve system stability.}

        \resumeItemListEnd
     \vspace{8pt}

\resumeProjectHeading
    {\textbf{English Vocabulary Learning App} $|$ \emph{Python, Tkinter, JSON}}{\emph{Jun 2025}}
    \resumeItemListStart
   \vspace{6pt}
        \resumeItem{\textbf{Project Overview:} Developed a desktop application to help users learn and manage English vocabulary with basic learning and lookup features.}

        \resumeItem{Built the application using \textbf{Python (Tkinter)}, applying \textbf{OOP principles} to organize code into manageable components.}
        
        \resumeItem{Developed \textbf{CRUD functionality} to manage \textbf{500+ vocabulary entries} using a \textbf{JSON-based storage system}.}
        
        \resumeItem{Used \textbf{API calls} and basic web crawling to enrich vocabulary data.}
        
        \resumeItem{Built \textbf{user authentication and role-based access control (Admin/User)}.}
        
        \resumeItem{Handled issues during file read/write operations to improve basic \textbf{data consistency} and application stability.}
        
        \resumeItem{Designed \textbf{5+ UI screens} (login, dashboard, vocabulary management) for a simple and user-friendly experience.}
        
        \resumeItem{Packaged the application into a standalone executable and received a \textbf{perfect practical score}.}

    \resumeItemListEnd

    \resumeSubHeadingListEnd
          \vspace{8pt}

             \vspace{4pt}
        
    
    \emph{If you’d like to explore my projects in detail, check out my GitHub: \href{https://github.com/nhiney?tab=repositories}{\underline{https://github.com/nhiney?tab=repositories}}.}

\vspace{4pt}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Ho Chi Minh City University of Industry and Trade}{Ho Chi Minh City, Vietnam}
        {Bachelor of Information Technology $|$ GPA: \textbf{3.34 / 4.0}}{Expected: 2027}
        \resumeItemListStart
            \resumeItem{Relevant coursework: Data Structures \& Algorithms, Database Systems, Software Engineering, Web Development, Object-Oriented Programming, Computer Networks.}
            
            \resumeItem{Participated in academic projects and competitions, contributing to system design and backend development.}
            
            \resumeItem{Often took the \textbf{team lead role}, coordinating tasks and supporting team members during development and testing.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
